### 2021-04-04 ms/suppmat.tex
Add changes up to ICES JMS submission

We incorporated the uncertainty in the conversion from size group (small and large returns) to age class (1SW and 2SW returns) by 
approximating the variance of log return abundance of each maiden age class 1SW and 2SW by assuming that the probability 
of the true number of returns of a given age, river, year, and size group ($N_{r,t,s,a}$) can be derived from a hypergeometric distribution

\begin{equation}
p[N_{r,t,s,a}|0:N_{r,t,s}] \sim Hypergeometric(n_{r,t,s}, 0:N_{r,t,s}, N_{r,t,s}:0, n_{r,t,s,a}),
\end{equation}

where $n_{r,t,s,a}$ is the number of scale samples in river r, year t, of returning age a, and of size group s;
$n_{r,t,s}$ is the total number of scale samples in river r, year t, and of size group s; and
$N_{r,t,s}$ is the total number of returns in river, year t, and of size group s.

We therefore obtain a vector of the probabilities of the returns of a given river r, year t, size group s and age a (i.e. $N_{r,t,s,a}$)
across the whole range of potential values, i.e. from zero to $N_{r,t,s}$, which provides the weighting probabilities to generate 10,000 random draws of $N_{r,t,s,a}$. 
We then add the draws of the same age from both size groups:
to obtain the estimates of number of returns of a given age a (i.e. 1SW or 2SW) for a given river and year ($N_{r,t,a}$):

\begin{equation}
N_{r,t,a} = N_{r,t,a,s=small}+ N_{r,t,a,s=large}.
\end{equation}

Lastly, as the coefficient of variation are comparable to standard deviations of less than 0.3 in the log-scale, we obtain
the estimate of $\epsilon_{r,t,a}$ as

\begin{equation}
\epsilon_{r,t,a} \approx \sigma_{log(N_{r,t,a})}.
\end{equation}

>>>>

We incorporated the uncertainty in the conversion from size group (small and large returns) to age class (1SW and 2SW returns) by 
approximating the variance of log return abundances of each maiden age class (i.e. 1SW and 2SW) assuming that the probability 
of the true number of returns of a given age, river, year, and size group ($N_{r,t,s,a}$) can be derived by bootstrapping a distribution
of number of returns from the hypergeometric distribution

% \begin{equation}
% p[N_{r,t,s,a}|0:N_{r,t,s}] \sim Hypergeometric(n_{r,t,s}, 0:N_{r,t,s}, N_{r,t,s}:0, n_{r,t,s,a}),
% \end{equation}

\begin{equation}
P(N_{obs,r,t,s,a}|n_{r,t,s,a}) \sim Hypergeometric(N_{r,t,s,a}, N_{r,t,s} - N_{r,t,s,a}, n_{r,t,s}),
\end{equation}

where $P(N_{obs,r,t,s,a}|n_{r,t,s,a})$ is the probability of having a specific number of returns $N_{r,t,s,a}$ given 
$n_{r,t,s,a}$, which is the number of scale samples in river r, year t, of returning age a, and of size group s;
$N_{r,t,s}$ is the total number of returns in river r, year t, and of size group s;
$N_{r,t,s} - N_{r,t,s,a}$ is the total numbers of returns in river r, year t, of size group s that are \textbf{not} of returning age a;
and $n_{r,t,s}$ is the total number of scale samples in river r, year t, and of size group s.
We iterated through all possible values of $N_{r,t,s,a}$ (i.e. from zero to $N_{r,t,s}$), to obtain a probavility for each value, which
we then used as weighting probabilities to sample 10,000 random draws of $N_{r,t,s,a}$, which we denote as $\hat{N}_{r,t,s,a}$. 
We then add the draws of the same age from both size groups to obtain a vector of estimates of number of returns of a given age a (i.e. 1SW or 2SW) for a given river and year ($\hat{N}_{r,t,a}$):

% k is the number of successes ($n_{r,t,s,a}$) (successes)
% N is the total number of individuals of size s ($N_{r,t,s}$) (total count) 
% K is the number of age a individual of size s ($N_{r,t,s,a}$) (total successes)
% n is the total number of scale samples ($n_{r,t,s}$) (trials)

% where $n_{r,t,s,a}$ is the number of scale samples in river r, year t, of returning age a, and of size group s;
% $n_{r,t,s}$ is the total number of scale samples in river r, year t, and of size group s; and
% $N_{r,t,s}$ is the total number of returns in river, year t, and of size group s.

% We therefore obtain a vector of the probabilities of the returns of a given river r, year t, size group s and age a (i.e. $N_{r,t,s,a}$)
% across the whole range of potential values, i.e. from zero to $N_{r,t,s}$, which provides the weighting probabilities to generate 10,000 random draws of $N_{r,t,s,a}$.

\begin{equation}
    \hat{N}_{r,t,a} = \hat{N}_{r,t,a,s=small }+ \hat{N}_{r,t,a,s=large}.
\end{equation}

Lastly, we obtain the estimates of $\epsilon_{r,t,a}$ by calculating the standard deviation of log-transformed $\hat{N}_{r,t,a}$:

\begin{equation}
\epsilon_{r,t,a} = \sigma_{log(\hat{N}_{r,t,a})}.
\end{equation}
